Future Directions

### 2021-03-09 manuscripts/laplacian_smoothing/arXiv/appendix.tex
Completed restatement of testing results. Changed appendix to match new statements.

\paragraph{Pointwise evaluation of Sobolev functions.}
First, however, as promised in our main text we clarify what is meant by pointwise evaluation of the regression function $f_0$. Strictly speaking, each $f \in H^1(X)$ is really an equivalence class, defined only up to sets of Lebesgue measure 0. In order to make sense of the evaluation $x \mapsto f(x)$, one must therefore pick a representative $f^{\star} \in f$. When $d = 1$, this is resolved in a standard way---since $H^1(\mc{X})$ embeds continuously into $C^0(\mc{X})$, there exists a continuous version of every $f \in H^1(\mc{X})$, and we take this continuous version as the representative $f^{\star}$. On the other hand, when $d \geq 2$, the Sobolev space $H^1(\mc{X})$ does not continuously embed into $C^0(\mc{X})$, and we must choose representatives in a different manner. In this case we let $f^{\star}$ be the precise representative \citep{evans15}, defined pointwise at points $x \in \mc{X}$ as
\begin{equation*}
f^{\star}(x) = 
\begin{dcases*}
\lim_{\varepsilon \to 0} \frac{1}{\nu(B(x,\varepsilon))} \int_{B(x,\varepsilon)} f(x) dx,&~~\textrm{if the limit exists,} \\
0,&~~\textrm{otherwise.}
\end{dcases*}
\end{equation*}
Note that when $d = 1$, the precise representative of any $f \in H^1(\mc{X})$ is continuous.

@@

In Lemma~\ref{lem:linear_smoother_fixed_graph_testing}, we upper bound the error of a test involving the statistic $\|\wc{f}\|_2^2 = {\bf Y}^{\top} S^2 {\bf Y}$. We will require that $S$ be a \emph{contraction}, meaning that it has operator norm no greater than $1$, $\|Sv\|_2 \leq \|v\|_2$ for all $v \in \Reals^n$.
\begin{lemma}
	\label{lem:linear_smoother_fixed_graph_testing}
	Let $\wc{T} = {\bf Y}^{\top} S^2 {\bf Y}$ for a square, symmetric matrix $S \in \Reals^{n \times n}$. Suppose $S$ is a contraction. Define the threshold $\wc{t}_b$ to be 
	\begin{equation}
	\label{eqn:linear_smoother_fixed_graph_threshold}
	\wc{t}_{b} := \norm{\lambdavec(S)}_2^2 + 2b \norm{\lambdavec(S)}_4^2.
	\end{equation}
	It holds that:
	\begin{itemize}
		\item \textbf{Type I error.}
		\begin{equation}
		\label{eqn:linear_smoother_fixed_graph_testing_typeI}
		\Pbb_0\bigl(\wc{T} > \wc{t}_b\bigr) \leq \frac{1}{b^2}.
		\end{equation}
		\item \textbf{Type II error.} Under the further assumption
		\begin{equation}
		\label{eqn:linear_smoother_fixed_graph_testing_critical_radius}
		f_0^{\top} S^2 f_0 \geq 4b \norm{\lambdavec(S)}_4^2,
		\end{equation}
		then
		\begin{equation}
		\label{eqn:linear_smoother_fixed_graph_testing_typeII}
		\Pbb_{f_0}\bigl(\wc{T} \leq \wc{t}_b\bigr) \leq \frac{4}{b^2} + \frac{8}{b \norm{\lambdavec(S)}_4^{2}}.
		\end{equation}
	\end{itemize}
\end{lemma}

@@

We now establish the upper bound~\eqref{eqn:linear_smoother_fixed_graph_testing_typeII} on Type II error. From assumption~\eqref{eqn:linear_smoother_fixed_graph_testing_critical_radius}, we see that $f_0^{\top} S^2 f_0^{\top} - \wc{t}_b \leq 0$. As a result,
\begin{align*}
\Pbb_{f_0}\Bigl(\wc{T} \leq \wc{t}_b\Bigr) & = \Pbb_{f_0}\Bigl(\wc{T} - \Ebb_{f_0}\bigl[\wc{T}\bigr] \leq \wc{t}_b - \Ebb_{f_0}\bigl[\wc{T}\bigr]\Bigr) \\ 
& \leq \Pbb_{f_0}\Bigl(\Bigl|\wc{T} - \Ebb_{f_0}\bigl[\wc{T}\bigr]\Bigr| \geq \Bigl|\wc{t}_b - \Ebb_{f_0}\bigl[\wc{T}\bigr]\Bigr|\Bigr) \\ 
& \leq \frac{\Var_{f_0}\bigl[\wc{T}\bigr]}{\bigl(\wc{t}_b - \Ebb_{f_0}\bigl[\wc{T}\bigr]\bigr)^2},
\end{align*}
where the last line follows from Chebyshev's inequality. Plugging in the expressions~\eqref{pf:linear_smoother_fixed_graph_testing_mean} and~\eqref{pf:linear_smoother_fixed_graph_testing_var} for the mean and variance of $\wc{T}$, as well as the definition of $\wc{t}_b$ in~\eqref{eqn:linear_smoother_fixed_graph_threshold}, we obtain that
\begin{equation}
\label{pf:linear_smoother_fixed_graph_testing2}
\Pbb_{f_0}\Bigl(\wc{T} \leq \wc{t}_b\Bigr) \leq \frac{4\|\lambdavec(S)\|_4^4}{\bigl(f_0^{\top}S^2f_0 - 2b \norm{\lambdavec(S)}_4^2\bigr)^2} + \frac{8f_0^{\top}S^4f_0 }{\bigl(f_0^{\top}S^2f_0 - 2b \norm{\lambdavec(S)}_4^2\bigr)^2}.
\end{equation}
We now use the assumed lower bound $f_0^{\top} S^2 f_0 \geq 4b \norm{\lambdavec(S)}_4^2$ to separately upper bound each of the two terms on the right hand side of~\eqref{pf:linear_smoother_fixed_graph_testing2}. It follows immediately that
\begin{equation}
\label{pf:linear_smoother_fixed_graph_testing2.5}
\frac{4 \|\lambdavec(S)\|_4^4}{\bigl(f_0^{\top}S^2f_0 - 2b \norm{\lambdavec(S)}_4^2\bigr)^2} \leq \frac{1}{b^2},
\end{equation}
giving a sufficient upper bound on the first term. Now we upper bound the second term,
\begin{equation}
\label{pf:linear_smoother_fixed_graph_testing3}
\frac{8f_0^{\top}S^4f_0 }{\bigl(f_0^{\top}S^2f_0 - 2b \norm{\lambdavec(S)}_4^2\bigr)^2} \leq \frac{32 f_0^{\top}S^4f_0 }{\bigl(f_0^{\top}S^2f_0\bigr)^2} \leq \frac{8}{b \|\lambdavec(S)\|_4^2} \frac{f_0^{\top}S^4f_0 }{f_0^{\top}S^2f_0} \leq \frac{8}{b \|\lambdavec(S)\|_4^2},
\end{equation}
where the final inequality is satisfied because $S$ is a contraction. Plugging~\eqref{pf:linear_smoother_fixed_graph_testing2.5} and~\eqref{pf:linear_smoother_fixed_graph_testing3} back into~\eqref{pf:linear_smoother_fixed_graph_testing2} then gives the desired result.\\
%\sbcomment{I think the first equality should be the negative of what you wrote?} \\
%\agcomment{You were correct. However I also rewrote the proof a bit to make it (hopefully) easier to follow. We also need that $S$ is a contraction---a condition that I had and then deleted at some point by accident--- and I added this to the statement of the Lemma.} 
\subsection{Analysis of Laplacian smoothing}

Upper bounds on the mean squared error of $\wh{f}$, and Type I and Type II error of $\wh{T}$, follow from setting $S = (\rho L + I)^{-1}$ in Lemmas~\ref{lem:linear_smoother_fixed_graph_estimation} and~\ref{lem:linear_smoother_fixed_graph_testing}. We give these results in Lemma~\ref{lem:ls_fixed_graph_estimation} and~\ref{lem:ls_fixed_graph_testing}, and prove them immediately. Recall that $\lambda_1,\ldots,\lambda_n$ are the $n$ eigenvalues of $\Lap$ (sorted in ascending order).
\begin{lemma}
	\label{lem:ls_fixed_graph_estimation}
	For any $\rho > 0$,
	\begin{equation}
	\label{eqn:ls_fixed_graph_estimation_prob}
	\frac{1}{n}\bigl\|\wh{f} - f_0\bigr\|_2^2 \leq \frac{2\rho}{n} \bigl(f_0^{\top} \Lap f_0\bigr) + \frac{10}{n}\sum_{k = 1}^{n} \frac{1}{\bigl(\rho \lambda_{k} + 1\bigr)^2},
	\end{equation}
	with probability at least $1 - \exp\Bigl(-\sum_{k = 1}^{n}\bigl(\rho \lambda_k + 1\bigr)^{-2}\Bigr)$.
\end{lemma}
Recall that 
\begin{equation*}
\wh{t}_b := \frac{1}{n}\sum_{k = 1}^{n} \frac{1}{\bigl(\rho \lambda_k + 1\bigr)^2} + \frac{2b}{n}\sqrt{\sum_{k = 1}^{n} \frac{1}{\bigl(\rho \lambda_k + 1\bigr)^4}}.
\end{equation*}
\begin{lemma}
	\label{lem:ls_fixed_graph_testing}
	For any $\rho > 0$ and any $b \geq 1$, it holds that:
	\begin{itemize}
		\item \textbf{Type I error.}
		\begin{equation}
		\label{eqn:ls_fixed_graph_testing_typeI}
		\Pbb_0\Bigl(\wh{T} > \wh{t}_b\Bigr) \leq \frac{1}{b^2}.
		\end{equation}
		\item \textbf{Type II error.} If
		\begin{equation}
		\label{eqn:ls_fixed_graph_testing_critical_radius}
		\frac{1}{n}\norm{f_0}_2^2 \geq \frac{2 \rho}{n} \bigl(f_0^{\top} \Lap f_0\bigr) + \frac{4b}{n} \Biggl(\sum_{k = 1}^{n} \frac{1}{(\rho\lambda_k + 1)^4} \Biggr)^{1/2},
		\end{equation}
		then
		\begin{equation}
		\label{eqn:ls_fixed_graph_testing_typeII}
		\Pbb_{f_0}\Bigl(\wh{T}(G) \leq \wh{t}_b\Bigr) \leq \frac{4}{b^2} + \frac{8}{b} \Biggl(\sum_{k = 1}^{n} \frac{1}{(\rho\lambda_k + 1)^4} \Biggr)^{-1/2}.
		\end{equation}
	\end{itemize}
\end{lemma}

\paragraph{Proof of Lemma~\ref{lem:ls_fixed_graph_estimation}.}
Let $\wh{S} = (\Id + \rho \Lap)^{-1}$, the estimator $\wh{f} = \wh{S}Y$, and
\begin{equation*}
\bigl\|\lambdavec(\wh{S})\bigr\|_2^2 = \sum_{k = 1}^{n} \frac{1}{\bigl(1 + \rho \lambda_k\bigr)^2}.
\end{equation*} 
We deduce the following upper bound on the bias term,
\begin{equation*}
\begin{aligned}
\bigl\|(\wh{S} - I)f_0\bigr\|_2^2 & = f_0^{\top} \Lap^{1/2} \Lap^{-1/2}\bigl(\wh{S} - \Id\bigr)^2 \Lap^{-1/2} \Lap^{1/2} f_0 \\
& \leq f_0^{\top} \Lap f_0 \cdot \lambda_n\Bigl(\Lap^{-1/2}\bigl(\wh{S} - \Id\bigr)^2 \Lap^{-1/2}\Bigr) \\
& = f_0^{\top} \Lap f_0 \cdot \max_{k \in [n]} \biggl\{\frac{1}{\lambda_k} \Bigl(1 - \frac{1}{\rho\lambda_k + 1}\Bigr)^2 \biggr\} \\
& \leq f_0^{\top} \Lap f_0 \cdot \rho.
\end{aligned}
\end{equation*} 
In the above, we have written $\Lap^{-1/2}$ for the square root of the pseudoinverse of $\Lap$, and the maximum is over all indices $k$ such that $\lambda_k > 0$. The claim of the Lemma then follows from Lemma~\ref{lem:linear_smoother_fixed_graph_estimation}.

\paragraph{Proof of Lemma~\ref{lem:ls_fixed_graph_testing}.}
Let $\wh{S} := (I + \rho L)^{-1}$, so that $\wh{T} = \frac{1}{n}{\bf Y}^{\top} \wh{S}^2 {\bf Y}$. Note that $\wh{S}$ is a contraction, so that we may invoke Lemma~\ref{lem:linear_smoother_fixed_graph_testing}. The bound on Type I error \eqref{eqn:ls_fixed_graph_testing_typeI} follows immediately from \eqref{eqn:linear_smoother_fixed_graph_testing_typeI}. 
To establish the bound on Type II error, we must lower bound $f_0^{\top} \wh{S}^2 f_0$. We first note that by assumption \eqref{eqn:ls_fixed_graph_testing_critical_radius},
\begin{align*}
f_0^{\top} \wh{S}^2 f_0 & = \bigl\|f_0\bigr\|_2^2 - f_0^{\top}(I - \wh{S}^2)f_0 \\
& \geq 2 \rho \bigl(f_0^{\top} \Lap f_0\bigr) - f_0^{\top}\bigl(I - \wh{S}^2\bigr)f_0 + 4b \Biggl(\sum_{k = 1}^{n} \frac{1}{(\rho\lambda_k + 1)^4} \Biggr)^{-1/2}.
\end{align*}
Upper bounding $f_0^{\top}\bigl(I - \wh{S}^2\bigr)f_0$ as follows:
\begin{equation*}
\begin{aligned}
f_0^{\top} \Bigl(\Id - \wh{S}^2\Bigr) f_0  & = f_0^{\top} \Lap^{1/2} \Lap^{-1/2}\Bigl(\Id - \wh{S}^2\Bigr) \Lap^{-1/2} \Lap^{1/2} f_0 \\ 
& \leq f_0^{\top} \Lap f_0 \cdot  \lambda_{n}\biggl(\Lap^{-1/2}\Bigl(\Id - \wh{S}^2\Bigr) \Lap^{-1/2}\biggr) \\ 
& = f_0^{\top} \Lap f_0 \cdot \max_{k} \biggl\{ \frac{1}{\lambda_k} \Bigl(1 - \frac{1}{(\rho \lambda_k + 1)^2}\Bigr) \biggr\} \\
& \leq f_0^{\top} \Lap f_0 \cdot 2\rho,
\end{aligned}
\end{equation*}
---where in the above the maximum is over all indices $k$ such that $\lambda_k > 0$, and the last inequality follows from the basic algebraic identity $1 - 1/(1 + x)^2 \leq 2 x$ for any $x > 0$ \sbcomment{You've used this before, so maybe move this comment earlier?}---we deduce that
\begin{equation*}
f_0^{\top} \wh{S}^2 f_0 \geq 4b \biggl(\sum_{k = 1}^{n} \frac{1}{(\rho\lambda_k + 1)^4} \biggr)^{-1/2}.
\end{equation*} 
The upper bound on Type II error \eqref{eqn:ls_fixed_graph_testing_typeII} then follows from Lemma~\ref{lem:linear_smoother_fixed_graph_testing}.

@@

Now, we would like to invoke Lemma~\ref{lem:ls_fixed_graph_testing}, and in order to do so, we must show that the inequality \eqref{eqn:ls_fixed_graph_testing_critical_radius} is satisfied with respect to $G = G_{n,r}$. First, we upper bound the right hand side of this inequality. Set $\wt{\rho} = M^{-8/(4 + d)}n^{-4/(4 + d)}$ as prescribed by Theorem~\ref{thm:laplacian_smoothing_testing}, it follows from \eqref{eqn:graph_sobolev_seminorm} and \eqref{eqn:neighborhood_eigenvalue} that
\begin{align*}
\frac{2 \rho}{n} \bigl(f_0^{\top} \Lap f_0\bigr) + \frac{4b}{n} \biggl(\sum_{k = 1}^{n} \frac{1}{(\rho\lambda_k + 1)^4} \biggr)^{1/2} & \leq C_2b\wt{\rho}M^2 + \frac{4b}{n}\Biggl[1 + \frac{1}{c_3^2}\biggl(\sum_{k = 2}^{n} \frac{1}{(\wt{\rho}k^{2/d} + 1)^4} \biggr)^{1/2} + \frac{r^4n^{1/2}}{c_3^2\wt{\rho}^2}\Biggr] \\
& \leq C_2b\wt{\rho}M^2 + \frac{4b}{n}\biggl(1 + \frac{\sqrt{2}}{c_3^{2}}\wt{\rho}^{-d/4} + \frac{r^4n^{1/2}}{c_3^2\wt{\rho}^2}\biggr) \\ 
& \leq \Bigl(C_2 + 4 + \frac{4\sqrt{2}}{c_3^{2}} + \frac{4}{c_3^2}\Bigr)bM^{2d/(4 + d)} n^{-4/(4 + d)}.
\end{align*}
The second inequality in the above is justified by Lemma~\ref{lem:variance_term_testing}, keeping in mind that $M \leq M_{\max}(d)$ implies that $\wt{\rho}^{-d/2} \leq n$. The third inequality follows from the upper bound on $r$ assumed in~\ref{asmp:ls_kernel_radius_testing} as well as the fact that $M \geq n^{-1/2}$.

>>>>

\paragraph{Pointwise evaluation of Sobolev functions.}
First, however, as promised in our main text we clarify what is meant by pointwise evaluation of the regression function $f_0$. Strictly speaking, each $f \in H^1(X)$ is really an equivalence class, defined only up to sets of Lebesgue measure 0. In order to make sense of the evaluation $x \mapsto f(x)$, one must therefore pick a representative $f^{\star} \in f$. When $d = 1$, this is resolved in a standard way---since $H^1(\mc{X})$ embeds continuously into $C^0(\mc{X})$, there exists a continuous version of every $f \in H^1(\mc{X})$, and we take this continuous version as the representative $f^{\star}$. On the other hand, when $d \geq 2$, the Sobolev space $H^1(\mc{X})$ does not continuously embed into $C^0(\mc{X})$, and we must choose representatives in a different manner. In this case we let $f^{\star}$ be the precise representative \citep{evans15}, defined pointwise at points $x \in \mc{X}$ as
\begin{equation*}
f^{\star}(x) = 
\begin{dcases*}
\lim_{\varepsilon \to 0} \frac{1}{\nu(B(x,\varepsilon))} \int_{B(x,\varepsilon)} f(z) dz,&~~\textrm{if the limit exists,} \\
0,&~~\textrm{otherwise.}
\end{dcases*}
\end{equation*}
Note that when $d = 1$, the precise representative of any $f \in H^1(\mc{X})$ is continuous.

@@

In Lemma~\ref{lem:linear_smoother_fixed_graph_testing}, we upper bound the error of a test involving the statistic $\|\wc{f}\|_2^2 = {\bf Y}^{\top} S^2 {\bf Y}$. We will require that $S$ be a \emph{contraction}, meaning that it has operator norm no greater than $1$, $\|Sv\|_2 \leq \|v\|_2$ for all $v \in \Reals^n$.
\begin{lemma}
	\label{lem:linear_smoother_fixed_graph_testing}
	Let $\wc{T} = {\bf Y}^{\top} S^2 {\bf Y}$ for a square, symmetric matrix $S \in \Reals^{n \times n}$. Suppose $S$ is a contraction. Define the threshold $\wc{t}_{\alpha}$ to be 
	\begin{equation}
	\label{eqn:linear_smoother_fixed_graph_threshold}
	\wc{t}_{\alpha} := \norm{\lambdavec(S)}_2^2 + \sqrt{\frac{2}{\alpha}} \norm{\lambdavec(S)}_4^2.
	\end{equation}
	It holds that:
	\begin{itemize}
		\item \textbf{Type I error.}
		\begin{equation}
		\label{eqn:linear_smoother_fixed_graph_testing_typeI}
		\Pbb_0\bigl(\wc{T} > \wc{t}_{\alpha}\bigr) \leq \alpha.
		\end{equation}
		\item \textbf{Type II error.} Under the further assumption
		\begin{equation}
		\label{eqn:linear_smoother_fixed_graph_testing_critical_radius}
		f_0^{\top} S^2 f_0 \geq \Bigl(2\sqrt{\frac{2}{\alpha}} + 2b\Bigr) \cdot \norm{\lambdavec(S)}_4^2,
		\end{equation}
		then
		\begin{equation}
		\label{eqn:linear_smoother_fixed_graph_testing_typeII}
		\Pbb_{f_0}\bigl(\wc{T} \leq \wc{t}_{\alpha}\bigr) \leq \frac{1}{b^2} + \frac{16}{b \norm{\lambdavec(S)}_4^{2}}.
		\end{equation}
	\end{itemize}
\end{lemma}

@@

We now establish the upper bound~\eqref{eqn:linear_smoother_fixed_graph_testing_typeII} on Type II error. From assumption~\eqref{eqn:linear_smoother_fixed_graph_testing_critical_radius}, we see that $f_0^{\top} S^2 f_0^{\top} - \wc{t}_{\alpha} \leq 0$. As a result,
\begin{align*}
\Pbb_{f_0}\Bigl(\wc{T} \leq \wc{t}_{\alpha}\Bigr) & = \Pbb_{f_0}\Bigl(\wc{T} - \Ebb_{f_0}\bigl[\wc{T}\bigr] \leq \wc{t}_{\alpha} - \Ebb_{f_0}\bigl[\wc{T}\bigr]\Bigr) \\ 
& \leq \Pbb_{f_0}\Bigl(\Bigl|\wc{T} - \Ebb_{f_0}\bigl[\wc{T}\bigr]\Bigr| \geq \Bigl|\wc{t}_{\alpha} - \Ebb_{f_0}\bigl[\wc{T}\bigr]\Bigr|\Bigr) \\ 
& \leq \frac{\Var_{f_0}\bigl[\wc{T}\bigr]}{\bigl(\wc{t}_{\alpha} - \Ebb_{f_0}\bigl[\wc{T}\bigr]\bigr)^2},
\end{align*}
where the last line follows from Chebyshev's inequality. Plugging in the expressions~\eqref{pf:linear_smoother_fixed_graph_testing_mean} and~\eqref{pf:linear_smoother_fixed_graph_testing_var} for the mean and variance of $\wc{T}$, as well as the definition of $\wc{t}_{\alpha}$ in~\eqref{eqn:linear_smoother_fixed_graph_threshold}, we obtain that
\begin{equation}
\label{pf:linear_smoother_fixed_graph_testing2}
\Pbb_{f_0}\Bigl(\wc{T} \leq \wc{t}_{\alpha}\Bigr) \leq \frac{4\|\lambdavec(S)\|_4^4}{\bigl(f_0^{\top}S^2f_0 - \sqrt{2/\alpha} \norm{\lambdavec(S)}_4^2\bigr)^2} + \frac{8f_0^{\top}S^4f_0 }{\bigl(f_0^{\top}S^2f_0 - \sqrt{2/\alpha} \norm{\lambdavec(S)}_4^2\bigr)^2}.
\end{equation}
We now use the assumed lower bound $f_0^{\top} S^2 f_0 \geq (2\sqrt{2/\alpha} + 2b) \norm{\lambdavec(S)}_4^2$ to separately upper bound each of the two terms on the right hand side of~\eqref{pf:linear_smoother_fixed_graph_testing2}. It follows immediately that
\begin{equation}
\label{pf:linear_smoother_fixed_graph_testing2.5}
\frac{4 \|\lambdavec(S)\|_4^4}{\bigl(f_0^{\top}S^2f_0 - \sqrt{2/\alpha} \norm{\lambdavec(S)}_4^2\bigr)^2} \leq \frac{1}{b^2},
\end{equation}
giving a sufficient upper bound on the first term. Now we upper bound the second term,
\begin{equation}
\label{pf:linear_smoother_fixed_graph_testing3}
\frac{8f_0^{\top}S^4f_0 }{\bigl(f_0^{\top}S^2f_0 - \sqrt{2/\alpha} \norm{\lambdavec(S)}_4^2\bigr)^2} \leq \frac{32 f_0^{\top}S^4f_0 }{\bigl(f_0^{\top}S^2f_0\bigr)^2} \leq \frac{16}{b \|\lambdavec(S)\|_4^2} \frac{f_0^{\top}S^4f_0 }{f_0^{\top}S^2f_0} \leq \frac{16}{b \|\lambdavec(S)\|_4^2},
\end{equation}
where the final inequality is satisfied because $S$ is a contraction. Plugging~\eqref{pf:linear_smoother_fixed_graph_testing2.5} and~\eqref{pf:linear_smoother_fixed_graph_testing3} back into~\eqref{pf:linear_smoother_fixed_graph_testing2} then gives the desired result.\\
%\sbcomment{I think the first equality should be the negative of what you wrote?} \\
%\agcomment{You were correct. However I also rewrote the proof a bit to make it (hopefully) easier to follow. We also need that $S$ is a contraction---a condition that I had and then deleted at some point by accident--- and I added this to the statement of the Lemma.} 
\subsection{Analysis of Laplacian smoothing}

Upper bounds on the mean squared error of $\wh{f}$, and Type I and Type II error of $\wh{T}$, follow from setting $S = (\rho L + I)^{-1}$ in Lemmas~\ref{lem:linear_smoother_fixed_graph_estimation} and~\ref{lem:linear_smoother_fixed_graph_testing}. We give these results in Lemma~\ref{lem:ls_fixed_graph_estimation} and~\ref{lem:ls_fixed_graph_testing}, and prove them immediately. Recall that $\lambda_1,\ldots,\lambda_n$ are the $n$ eigenvalues of $\Lap$ (sorted in ascending order).
\begin{lemma}
	\label{lem:ls_fixed_graph_estimation}
	For any $\rho > 0$,
	\begin{equation}
	\label{eqn:ls_fixed_graph_estimation_prob}
	\frac{1}{n}\bigl\|\wh{f} - f_0\bigr\|_2^2 \leq \frac{2\rho}{n} \bigl(f_0^{\top} \Lap f_0\bigr) + \frac{10}{n}\sum_{k = 1}^{n} \frac{1}{\bigl(\rho \lambda_{k} + 1\bigr)^2},
	\end{equation}
	with probability at least $1 - \exp\Bigl(-\sum_{k = 1}^{n}\bigl(\rho \lambda_k + 1\bigr)^{-2}\Bigr)$.
\end{lemma}
Recall that 
\begin{equation*}
\wh{t}_{\alpha} := \frac{1}{n}\sum_{k = 1}^{n} \frac{1}{\bigl(\rho \lambda_k + 1\bigr)^2} + \frac{1}{n}\sqrt{\frac{2}{\alpha}\sum_{k = 1}^{n} \frac{1}{\bigl(\rho \lambda_k + 1\bigr)^4}}.
\end{equation*}
\begin{lemma}
	\label{lem:ls_fixed_graph_testing}
	For any $\rho > 0$ and any $b \geq 1$, it holds that:
	\begin{itemize}
		\item \textbf{Type I error.}
		\begin{equation}
		\label{eqn:ls_fixed_graph_testing_typeI}
		\Pbb_0\Bigl(\wh{T} > \wh{t}_{\alpha}\Bigr) \leq \alpha.
		\end{equation}
		\item \textbf{Type II error.} If
		\begin{equation}
		\label{eqn:ls_fixed_graph_testing_critical_radius}
		\frac{1}{n}\norm{f_0}_2^2 \geq \frac{2 \rho}{n} \bigl(f_0^{\top} \Lap f_0\bigr) + \frac{2\sqrt{2/\alpha} + 2b}{n} \Biggl(\sum_{k = 1}^{n} \frac{1}{(\rho\lambda_k + 1)^4} \Biggr)^{1/2},
		\end{equation}
		then
		\begin{equation}
		\label{eqn:ls_fixed_graph_testing_typeII}
		\Pbb_{f_0}\Bigl(\wh{T}(G) \leq \wh{t}_{\alpha}\Bigr) \leq \frac{1}{b^2} + \frac{16}{b} \Biggl(\sum_{k = 1}^{n} \frac{1}{(\rho\lambda_k + 1)^4} \Biggr)^{-1/2}.
		\end{equation}
	\end{itemize}
\end{lemma}

\paragraph{Proof of Lemma~\ref{lem:ls_fixed_graph_estimation}.}
Let $\wh{S} = (\Id + \rho \Lap)^{-1}$, the estimator $\wh{f} = \wh{S}Y$, and
\begin{equation*}
\bigl\|\lambdavec(\wh{S})\bigr\|_2^2 = \sum_{k = 1}^{n} \frac{1}{\bigl(1 + \rho \lambda_k\bigr)^2}.
\end{equation*} 
We deduce the following upper bound on the bias term,
\begin{equation*}
\begin{aligned}
\bigl\|(\wh{S} - I)f_0\bigr\|_2^2 & = f_0^{\top} \Lap^{1/2} \Lap^{-1/2}\bigl(\wh{S} - \Id\bigr)^2 \Lap^{-1/2} \Lap^{1/2} f_0 \\
& \leq f_0^{\top} \Lap f_0 \cdot \lambda_n\Bigl(\Lap^{-1/2}\bigl(\wh{S} - \Id\bigr)^2 \Lap^{-1/2}\Bigr) \\
& = f_0^{\top} \Lap f_0 \cdot \max_{k \in [n]} \biggl\{\frac{1}{\lambda_k} \Bigl(1 - \frac{1}{\rho\lambda_k + 1}\Bigr)^2 \biggr\} \\
& \leq f_0^{\top} \Lap f_0 \cdot \rho.
\end{aligned}
\end{equation*} 
In the above, we have written $\Lap^{-1/2}$ for the square root of the pseudoinverse of $\Lap$, the maximum is over all indices $k$ such that $\lambda_k > 0$, and the last inequality follows from the basic algebraic identity $1 - 1/(1 + x)^2 \leq 2 x$ for any $x > 0$. The claim of the Lemma then follows from Lemma~\ref{lem:linear_smoother_fixed_graph_estimation}.

\paragraph{Proof of Lemma~\ref{lem:ls_fixed_graph_testing}.}
Let $\wh{S} := (I + \rho L)^{-1}$, so that $\wh{T} = \frac{1}{n}{\bf Y}^{\top} \wh{S}^2 {\bf Y}$. Note that $\wh{S}$ is a contraction, so that we may invoke Lemma~\ref{lem:linear_smoother_fixed_graph_testing}. The bound on Type I error \eqref{eqn:ls_fixed_graph_testing_typeI} follows immediately from \eqref{eqn:linear_smoother_fixed_graph_testing_typeI}. 
To establish the bound on Type II error, we must lower bound $f_0^{\top} \wh{S}^2 f_0$. We first note that by assumption \eqref{eqn:ls_fixed_graph_testing_critical_radius},
\begin{align*}
f_0^{\top} \wh{S}^2 f_0 & = \bigl\|f_0\bigr\|_2^2 - f_0^{\top}(I - \wh{S}^2)f_0 \\
& \geq 2 \rho \bigl(f_0^{\top} \Lap f_0\bigr) - f_0^{\top}\bigl(I - \wh{S}^2\bigr)f_0 +  \Bigl(2\sqrt{\frac{2}{\alpha}} + 2b\Bigr) \cdot \Biggl(\sum_{k = 1}^{n} \frac{1}{(\rho\lambda_k + 1)^4} \Biggr)^{-1/2}.
\end{align*}
Upper bounding $f_0^{\top}\bigl(I - \wh{S}^2\bigr)f_0$ as follows:
\begin{equation*}
\begin{aligned}
f_0^{\top} \Bigl(\Id - \wh{S}^2\Bigr) f_0  & = f_0^{\top} \Lap^{1/2} \Lap^{-1/2}\Bigl(\Id - \wh{S}^2\Bigr) \Lap^{-1/2} \Lap^{1/2} f_0 \\ 
& \leq f_0^{\top} \Lap f_0 \cdot  \lambda_{n}\biggl(\Lap^{-1/2}\Bigl(\Id - \wh{S}^2\Bigr) \Lap^{-1/2}\biggr) \\ 
& = f_0^{\top} \Lap f_0 \cdot \max_{k} \biggl\{ \frac{1}{\lambda_k} \Bigl(1 - \frac{1}{(\rho \lambda_k + 1)^2}\Bigr) \biggr\} \\
& \leq f_0^{\top} \Lap f_0 \cdot 2\rho,
\end{aligned}
\end{equation*}
---where in the above the maximum is over all indices $k$ such that $\lambda_k > 0$---we deduce that
\begin{equation*}
f_0^{\top} \wh{S}^2 f_0 \geq  \Bigl(2\sqrt{\frac{2}{\alpha}} + 2b\Bigr) \cdot \biggl(\sum_{k = 1}^{n} \frac{1}{(\rho\lambda_k + 1)^4} \biggr)^{-1/2}.
\end{equation*} 
The upper bound on Type II error \eqref{eqn:ls_fixed_graph_testing_typeII} then follows from Lemma~\ref{lem:linear_smoother_fixed_graph_testing}.

@@

Now, we would like to invoke Lemma~\ref{lem:ls_fixed_graph_testing}, and in order to do so, we must show that the inequality \eqref{eqn:ls_fixed_graph_testing_critical_radius} is satisfied with respect to $G = G_{n,r}$. First, we upper bound the right hand side of this inequality. Setting $\wt{\rho} = M^{-8/(4 + d)}n^{-4/(4 + d)}$ as prescribed by Theorem~\ref{thm:laplacian_smoothing_testing}, it follows from \eqref{eqn:graph_sobolev_seminorm} and \eqref{eqn:neighborhood_eigenvalue} that
\begin{align*}
\frac{2 \rho}{n} \bigl(f_0^{\top} \Lap f_0\bigr) + \frac{2\sqrt{2/\alpha} + 2b}{n} \biggl(\sum_{k = 1}^{n} \frac{1}{(\rho\lambda_k + 1)^4} \biggr)^{1/2} & \leq C_2b\wt{\rho}M^2 + \frac{2\sqrt{2/\alpha} + 2b}{n}\Biggl[1 + \frac{1}{c_3^2}\biggl(\sum_{k = 2}^{n} \frac{1}{(\wt{\rho}k^{2/d} + 1)^4} \biggr)^{1/2} + \frac{r^4n^{1/2}}{c_3^2\wt{\rho}^2}\Biggr] \\
& \leq C_2b\wt{\rho}M^2 + \frac{2\sqrt{2/\alpha} + 2b}{n}\biggl(1 + \frac{\sqrt{2}}{c_3^{2}}\wt{\rho}^{-d/4} + \frac{r^4n^{1/2}}{c_3^2\wt{\rho}^2}\biggr) \\ 
& \leq \Bigl(C_2 + 2 + \frac{2\sqrt{2}}{c_3^{2}} + \frac{2}{c_3^2}\Bigr)\cdot \Bigl(\sqrt{\frac{2}{\alpha}} + b\Bigr) \cdot M^{2d/(4 + d)} n^{-4/(4 + d)}.
\end{align*}
The second inequality in the above is justified by Lemma~\ref{lem:variance_term_testing}, keeping in mind that $M \leq M_{\max}(d)$ implies that $\wt{\rho}^{-d/2} \leq n$. The third inequality follows from the upper bound on $r$ assumed in~\ref{asmp:ls_kernel_radius_testing} as well as the fact that $M \geq n^{-1/2}$.
